`forestecology` package for modeling interspecies competition between trees

### 2021-01-25 etc/paper/forestecology.Rmd
Added Simon as author
First pass at refactoring README
Renamed all objects to follow type_instance convention. Ex: growth_bw and growth_ex

@@

```{r bw-load-data}
data(bw_census_2008, bw_census_2014, bw_species)

# Append additional species data
bw_census_2008 <- bw_census_2008 %>%
  left_join(bw_species, by = "sp") %>%
  select(-c(genus, species, latin))
```

@@

@@

```{r bw-compute-growth}
bw_census_2014 <- bw_census_2014 %>%
  filter(!str_detect(codes, "R"))

bw_growth_df <-
  compute_growth(bw_census_2008, bw_census_2014, id = "treeID") %>%
  # Convert all variables denoting species to factors
  mutate(
    sp = sp %>% to_any_case() %>% as.factor(),
    species = sp,
    family = as.factor(family),
    trait_group = as.factor(trait_group)
  ) %>%
  # Drop unnecessary variables
  select(-stemID)
```

@@

First, we indicate which trees are part of the buffer. This necessitates information about the study region boundary. In this case, we use a `sf_polygon` object `bw_study_region` which comes pre-loaded in the `forestecology` packages. After loading `bw_study_region`, we illustrate the results of the `add_buffer_variable()` function in Figure \ref{fig:bw-define-buffer}. Trees on the periphery denote with lighter colors are part of the buffer and will not be considered as "focal" trees of interest going forward; they will only be considered as competitor trees.

```{r bw-define-buffer, out.width="100%", fig.cap="Buffer region for Big Woods study region."}
data(bw_study_region)

bw_growth_df <- bw_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, 
                      region = bw_study_region)

>>>>

- name: Simon P. Couch
  affiliation: Mathematics Department, Reed College

@@

```{r bw-load-data}
data(census_2008_bw, census_2014_bw, species_bw)

# Append additional species data
census_2008_bw <- census_2008_bw %>%
  left_join(species_bw, by = "sp") %>%
  select(-c(genus, species, latin))
```

@@

MERGE THIS SUBSECTION with previous?

@@

```{r bw-compute-growth}
census_2014_bw <- census_2014_bw %>%
  filter(!str_detect(codes, "R"))

bw_growth_df <-
  compute_growth(census_2008_bw, census_2014_bw, id = "treeID") %>%
  # Convert all variables denoting species to factors
  mutate(
    sp = sp %>% to_any_case() %>% as.factor(),
    species = sp,
    family = as.factor(family),
    trait_group = as.factor(trait_group)
  ) %>%
  # Drop unnecessary variables
  select(-stemID)
```

@@

First, we indicate which trees are part of the buffer. This necessitates information about the study region boundary. In this case, we use a `sf_polygon` object `study_region_bw` which comes pre-loaded in the `forestecology` packages. After loading `study_region_bw`, we illustrate the results of the `add_buffer_variable()` function in Figure \ref{fig:bw-define-buffer}. Trees on the periphery denote with lighter colors are part of the buffer and will not be considered as "focal" trees of interest going forward; they will only be considered as competitor trees.

```{r bw-define-buffer, out.width="100%", fig.cap="Buffer region for Big Woods study region."}
data(study_region_bw)

bw_growth_df <- bw_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, 
                      region = study_region_bw)
